Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-01 paper/paper.tex
Add dummy topology figure
Add start of query model section

Poor network scheduling can easily result in suboptimal query execution.
For example, consider the simple topology shown in XXXX.
Assume a query is being processed that requires data to be sent between hosts A and C and hosts B and D that together will use the full capacity of all links in the network.
If the flows have equal bandwidth requirements, then fair bandwidth allocation will perform well.
However, if the flow between A and C requires twice the bandwidth of the flow between B and D, the first flow will have a longer completion time while it waits for available bandwidth.

@@

>>>>

\begin{figure}
    \centering
    \missingfigure{Topology graph}
    \caption{Sample network topology}\label{fig:sample-topology}
\end{figure}

Poor network scheduling can easily result in suboptimal query execution.
For example, consider the simple topology shown in Figure~\ref{fig:sample-topology}.
Assume a query is being processed that requires data to be sent between hosts A and C and hosts B and D that together will use the full capacity of all links in the network.
If the flows have equal bandwidth requirements, then fair bandwidth allocation will perform well.
However, if the flow between A and C requires twice the bandwidth of the flow between B and D, the first flow will have a longer completion time while it waits for available bandwidth.

@@

\begin{figure}
    \centering
    \missingfigure{ER diagram}
    \caption{Simple query entities}\label{fig:entities}
\end{figure}

Our prototype system considers foreign key join queries between entity sets with a fixed join order and simple filtering on attributes of the first entity set.
For example, assume we have two entity sets \texttt{User} and \texttt{Item} with a one-to-many foreign key relating a user to each item as in Figure~\ref{fig:entities}.
A query (in SQL) syntax may look like \texttt{SELECT * FROM User, Item WHERE Item.User\_id = User.id AND Item.price > 20}.
In the future, we plan to consider a richer query language.
This will also present more interesting opportunities for optimization.

The execution model for these queries is very straightforward.
We consider the execution of the simple query given above.
We start by passing the query to each node which has entities of the class on the left side of the join (\texttt{Item}).
Those nodes will scan their local list of entities and apply the necessary filters (\texttt{price > 20}).
Each node then forwards the necessary foreign keys to nodes holding entites of the class on the right side of the join (\texttt{User}).
These nodes are then able to look up entities on the other side of the join and results can be passed back to the client.
